\section*{Material Safety Data Sheet}
\label{sec:MSDS}
\addcontentsline{toc}{section}{\nameref{sec:MSDS}}


\setlength{\columnsep}{30pt}
\begin{multicols*}{2}
\begin{flushleft}

\begin{sans}

\textbf{1. IDENTIFICATION OF THE SUBSTANCE/PREPARATION AND OF THE COMPANY/UNDERTAKING}\\
Product name: m-Cresol Purple sodium salt\\
Product Number: 211761\\
Company: Sigma-Aldrich\\
3050 Spruce Street\\
SAINT LOUIS, MO 63103\\
USA\\
Telephone: +18003255832\\
Fax: +18003255052\\
Emergency Phone: (314) 776-6555

\textbf{2. COMPOSITION/INFORMATION ON INGREDIENTS}\\
Synonyms: m-Cresolsulfonphthaleinsodium salt\\
Formula: \ce{C21H17NaO5S}\\
Molecular Weight: 404.41 g/mol\\
CAS-No. EC-No. Index-No. Classification Concentration\\
\textbf{m-Cresol Purple sodium salt}\\
62625-31-4 263-656-9 - - -

\textbf{3. HAZARDS IDENTIFICATION}\\
Not a hazardous substance or preparation according to EC-directives 67/548/EEC or 1999/45/EC.

\textbf{4. FIRST AID MEASURES}\\
\textbf{If inhaled}\\
If breathed in, move person into fresh air. If not breathing give artificial respiration.\\
\textbf{In case of skin contact}\\
Wash off with soap and plenty of water.\\
\textbf{In case of eye contact}\\
Flush eyes with water as a precaution.\\
\textbf{If swallowed}\\
Never give anything by mouth to an unconscious person. Rinse mouth with water.

\textbf{5. FIRE-FIGHTING MEASURES}\\
\textbf{Suitable extinguishing media}\\
Use water spray, alcohol-resistant foam, dry chemical or carbon dioxide.\\
\textbf{Special protective equipment for fire-fighters}\\
Wear self contained breathing apparatus for fire fighting if necessary.\\
Aldrich - 211761 \url{http://www.sigma-aldrich.com} Page 2 of 4.

\textbf{6. ACCIDENTAL RELEASE MEASURES}\\
\textbf{Personal precautions}\\
Avoid dust formation.\\
\textbf{Environmental precautions}\\
Do not let product enter drains.\\
\textbf{Methods for cleaning up}\\
Sweep up and shovel. Keep in suitable, closed containers for disposal.

\textbf{7. HANDLING AND STORAGE}\\
\textbf{Handling}\\
Provide appropriate exhaust ventilation at places where dust is formed. Normal measures for preventive fire protection.\\
\textbf{Storage}\\
Store in cool place. Keep container tightly closed in a dry and well-ventilated place.

\textbf{8. EXPOSURE CONTROLS/PERSONAL PROTECTION}\\
\textbf{Personal protective equipment}\\
\textbf{Respiratory protection}\\
Respiratory protection is not required. Where protection from nuisance levels of dusts are desired, use type N95 (US) or type P1 (EN 143) dust masks. Use respirators and components tested and approved under appropriate government standards such as NIOSH (US) or CEN (EU).\\
\textbf{Hand protection}\\
For prolonged or repeated contact use protective gloves.\\
\textbf{Eye protection}\\
Safety glasses.\\
\textbf{Hygiene measures}\\
General industrial hygiene practice.

\textbf{9. PHYSICAL AND CHEMICAL PROPERTIES}\\
\textbf{Appearance}\\
Form powder.\\
\textbf{Color}\\
Dark red\\
\textbf{Safety data}\\
pH: No data available.\\
Melting point: No data available.\\
Boiling point: No data available.\\
Flash point: No data available.\\
Ignition temperature: No data available.\\
Lower explosion limit: No data available.\\
Upper explosion limit: No data available.\\
Water solubility: No data available.

\textbf{10. STABILITY AND REACTIVITY}\\
Aldrich - 211761 \url{http://www.sigma-aldrich.com} Page 3 of 4.\\
\textbf{Storage stability}\\
Stable under recommended storage conditions.\\
\textbf{Materials to avoid}\\
Strong oxidizing agents.\\
\textbf{Hazardous decomposition products}\\
Hazardous decomposition products formed under fire conditions.
Carbon oxides, sulfur oxides

\textbf{11. TOXICOLOGICAL INFORMATION}\\
\textbf{Acute toxicity}\\
No data available.\\
\textbf{Irritation and corrosion}\\
No data available.\\
\textbf{Sensitization}\\
No data available.\\
\textbf{Chronic exposure}\\
IARC: No component of this product present at levels greater than or equal to 0.1\% is identified as probable, possible or confirmed human carcinogen by IARC.\\
\textbf{Potential Health Effects}\\
Inhalation: May be harmful if inhaled. May cause respiratory tract irritation.\\
Skin: May be harmful if absorbed through skin. May cause skin irritation.
Eyes: May cause eye irritation.\\
Ingestion: May be harmful if swallowed.

\textbf{12. ECOLOGICAL INFORMATION}\\
\textbf{Elimination information} (persistence and degradability)\\
No data available.\\
\textbf{Ecotoxicity effects}\\
No data available.\\
\textbf{Further information on ecology}\\
No data available.

\textbf{13. DISPOSAL CONSIDERATIONS}\\
\textbf{Product}\\
Observe all federal, state and local environmental regulations.\\
\textbf{Contaminated packaging}\\
Dispose of as unused product.

\textbf{TRANSPORT INFORMATION}\\
\textbf{ADR/RID}\\
Not dangerous goods.\\
\textbf{IMDG}\\
Not dangerous goods.\\
Aldrich - 211761 \url{http://www.sigma-aldrich.com} Page 4 of 4.\\
\textbf{IATA}\\
Not dangerous goods.

\textbf{REGULATORY INFORMATION}\\
\textbf{Labeling according to EC Directives}\\
Further information: The product does not need to be labeled in accordance with EC directives or respective national law.

\end{sans}
\end{flushleft}
\end{multicols*}