\section*{Warranty}
\label{sec:Warranty}
\addcontentsline{toc}{section}{\nameref{sec:Warranty}}

\begin{sans}

Sunburst Sensors, LLC warrants to the original purchaser that instruments manufactured by Sunburst Sensors shall be free from defects in materials and workmanship for the life of the product. Under this warranty, the instrument will be repaired or replaced as deemed appropriate by Sunburst Sensors without charge for parts or labor when the instrument is shipped prepaid to our location. This warranty does not apply to any instrument which has not been installed or used in accordance with proper operation and installation specifications. Sunburst reserves the right to void any warranty, written or implied, if upon Sunburst's examination of the instrument reveals failure was due solely, or in part, to accident, misuse, neglect, abuse, alteration, improper installation, unauthorized repair or improper testing by the buyer. Sunburst shall not be liable under any circumstances for indirect, special, consequential, or incidental damages in connection with, or arising out of, the sale, performance, or use of the instrument covered by this warranty. When a Product is returned to Sunburst Sensors for refurbishment/recalibration this service is considered normal preventative maintenance. Recalibration of your instrument shall not be treated as a warranty service unless recalibration of your instrument is required as the result of repairs to the instrument pursuant to this Warranty. Your instrument may only be repaired and refurbished by a certified, trained specialist from Sunburst Sensors, LLC. Breach of this requirement without prior consultation from Sunburst Sensors may result in the voiding of your Warranty. 

If you would like more information on your \instType{} for self-repair or refurbishment please contact Sunburst Sensors. After notification is given that the interior of the instrument will be accessed, Sunburst Sensors is no longer responsible for defects incurred under the by the user.

\end{sans}